Group 1: Tennis 

### 2019-12-12 Group1Prez.Rmd
Forgot to save before last commit
Updated slides and added graphics

## Tournament Results: Women
```{r, echo=FALSE}
Tourney1_Women = data.frame(`P(Winning a Rally)` = TDWomen[,1],
                            `Paper P(Winning the Tournement)` = c(.2872, .3599, .0482, .3074))
#`Our P(Winning the Tournement )` =round( pTC(TDWomen[1,1],TDWomen[2,1],TDWomen[3,1],TDWomen[4,1], 2), 4)

@@

## Tournament Results: Men
```{r, echo=FALSE}
Tourney1_Men = data.frame(`P(Winning a Rally)` = TDMen[,1],
                            `Paper P(Winning the Tournement)` = c(.6747, .0851, .0945, .1457))
#`Our P(Winning the Tournement )` =round( pTC(TDMen[1,1],TDMen[2,1],TDMen[3,1],TDMen[4,1], 2), 4)

@@

@@

```{r, warning=FALSE, echo=FALSE}
WimWomen <- read_csv("2019 Womens Wimbledon.csv")

@@

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") +
  ylab("P(Win the Tournement)")
  ggtitle("Which Player Won the Tournement?")

@@

@@

```{r, warning=FALSE, echo=FALSE}
WimMen <- read_csv("2019 Men's Wimbledon.csv")

@@

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq)) +
  xlab("Players") +
  ggtitle("Which Player Won the Tournement?")

@@

>>>>

## 2002 U.S Open: Women
```{r, echo=FALSE}
Tourney1_Women = data.frame(`P(Winning a Rally)` = TDWomen[,1],
                            `Paper P(Winning the Tournement)` = c(.2872, .3599, .0482, .3074))
#`Our P(Winning the Tournement )` =round( pTC(TDWomen[1,1],TDWomen[2,1],TDWomen[3,1],TDWomen[4,1], 2), 4)

@@

## 2002 U.S Open: Women

```{r,echo=FALSE, fig.align='center'}
include_graphics("Serena.png")
```

## 2002 U.S Open: Men
```{r, echo=FALSE, }
Tourney1_Men = data.frame(`P(Winning a Rally)` = TDMen[,1],
                            `Paper P(Winning the Tournement)` = c(.6747, .0851, .0945, .1457))
#`Our P(Winning the Tournement )` =round( pTC(TDMen[1,1],TDMen[2,1],TDMen[3,1],TDMen[4,1], 2), 4)

@@

##2002 U.S Open: Men

```{r,echo=FALSE, fig.align='center'}
include_graphics("Pete.png")
```

@@

```{r, warning=FALSE, echo=FALSE, message=FALSE}
WimWomen <- read_csv("2019 Womens Wimbledon.csv")

@@

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") +
  ylab("P(Win the Tournement)")+
  ggtitle("Which Player Won the Tournement?")

@@

```{r,echo=FALSE, fig.align='center'}
include_graphics("Simona.png")
```

@@

```{r, warning=FALSE, echo=FALSE, message=FALSE}
WimMen <- read_csv("2019 Men's Wimbledon.csv")

@@

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") +
   ylab("P(Win the Tournement)")+
  ggtitle("Which Player Won the Tournement?")

@@

## 2019 Wimbledon: Men 
```{r,echo=FALSE, fig.align='center'}
include_graphics("Novak.png")
```
